Author Gender and Outcomes

### 2019-08-02 figures/author_outcomes/supp_submission_outcomes.rmd

gender_outcomes <- elife %>%
  filter(initial_decision_made) %>%
  gather(author_key, value = gender, ca_gender, la_gender, fa_gender) %>%
  filter(gender %in% c('M', 'F')) %>%
  group_by(author_key) %>%
  mutate(
    # if not ocnsidering the corr. author, then the count is all full submissions, ie: for when a submission ia made
    total_papers = ifelse(author_key == "ca_gender", n(), sum(has_full_submission))
    )%>%
  group_by(author_key, gender) %>%
  summarize(
        paper_count = n(),
        accept_count = sum(accepted == TRUE, na.rm = T),
        encourage_count = sum(encouraged == TRUE),
        encourage_rate = ifelse(author_key[1] == "ca_gender", encourage_count / n(), NA),
        # this accept rate is the number of accepted papers / number of initial + full submissions
        accept_rate = ifelse(author_key[1] == "ca_gender", accept_count / sum(!has_full_submission | full_decision_made, na.rm = T), NA),
        submit_rate = n() / total_papers[1],
        # this is the number of accepted papers divided by all papers 
        encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  ungroup() %>%
  gather(measure_key, value = measurement, submit_rate, encourage_rate, accept_rate, encourage_accept_rate) %>%
  left_join(sig_df, by = c("measure_key", "author_key")) %>%
  mutate(
    author_key = factor(author_key,
                        levels = c("ca_gender", "fa_gender", "la_gender"),
                        labels = c("ca_gender" = "Corresponding", "fa_gender" = "First", "la_gender" = "Last")
                        ),
    measure_key = factor(measure_key, 
                         labels = c("submit_rate" = "Submissions", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted", "accept_rate" = "Overall accept %"),
                         levels = c("submit_rate", "encourage_rate", "encourage_accept_rate", "accept_rate")),
    gender = ifelse(gender == "F", "Female", "Male"),
    standard_error = 1.96 * sqrt( (measurement * (1 - measurement)) / paper_count),
    lower = measurement - standard_error,
    upper = measurement + standard_error
  ) %>%
  ggplot(aes(x = gender, y = measurement, color = factor(gender), shape = factor(gender), fill = factor(gender))) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  #geom_text(aes(y = 0.08, label = paper_count), size = 2.5, color = "black") +
  geom_text(aes(x = gender, y = measurement + 0.1, label = ifelse(sig %in% c("*", "**"), round(measurement, 3) * 100, "")), color = "black", size = 3) +
  #facet_grid(measure_key ~ author_key) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black") +
  # Plot the text for signif check. For final publication we decided to not draw text for N/A 
  geom_text(aes(x = 1.5, y = ifelse(sig == "N/A", 1.1, 0.95), label = ifelse(measure_key == "Submissions", "", as.character(sig))), color = "black") +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_grid(author_key ~ measure_key, switch = "y") +
  coord_cartesian(ylim = c(0, 1)) +
  scale_y_continuous(position = "right") +
  theme_dakota() +
  guides(fill = F) +
  labs(
    x = "Gender of Author",
    y = ""
  )

>>>>

gender_outcomes <- elife %>%
  filter(initial_decision_made) %>%
  gather(author_key, value = gender, ca_gender, la_gender, fa_gender) %>%
  filter(gender %in% c('M', 'F')) %>%
  group_by(author_key) %>%
  mutate(
    # if not ocnsidering the corr. author, then the count is all full submissions, ie: for when a submission ia made
    total_papers = ifelse(author_key == "ca_gender", n(), sum(has_full_submission))
    )%>%
  group_by(author_key, gender) %>%
  summarize(
        paper_count = n(),
        accept_count = sum(accepted == TRUE, na.rm = T),
        encourage_count = sum(encouraged == TRUE),
        encourage_rate = ifelse(author_key[1] == "ca_gender", encourage_count / n(), NA),
        # this accept rate is the number of accepted papers / number of initial + full submissions
        accept_rate = ifelse(author_key[1] == "ca_gender", accept_count / sum(!has_full_submission | full_decision_made, na.rm = T), NA),
        submit_rate = n() / total_papers[1],
        # this is the number of accepted papers divided by all papers 
        encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  ungroup() %>%
  gather(measure_key, value = measurement, submit_rate, encourage_rate, accept_rate, encourage_accept_rate) %>%
  left_join(sig_df, by = c("measure_key", "author_key")) %>%
  mutate(
    author_key = factor(author_key,
                        levels = c("ca_gender", "fa_gender", "la_gender"),
                        labels = c("ca_gender" = "Corresponding", "fa_gender" = "First", "la_gender" = "Last")
                        ),
    measure_key = factor(measure_key, 
                         labels = c("submit_rate" = "Submissions", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted", "accept_rate" = "Overall accept %"),
                         levels = c("submit_rate", "encourage_rate", "encourage_accept_rate", "accept_rate")),
    gender = ifelse(gender == "F", "Female", "Male"),
    standard_error = 1.96 * sqrt( (measurement * (1 - measurement)) / paper_count),
    lower = measurement - standard_error,
    upper = measurement + standard_error
  ) %>%
  ggplot(aes(x = gender, y = measurement, color = factor(gender), shape = factor(gender), fill = factor(gender))) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  #geom_text(aes(y = 0.08, label = paper_count), size = 2.5, color = "black") +
  geom_text(aes(x = gender, y = measurement + 0.1, label = ifelse(sig %in% c("*", "**", "***"), round(measurement, 3) * 100, "")), color = "black", size = 3) +
  #facet_grid(measure_key ~ author_key) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black") +
  # Plot the text for signif check. For final publication we decided to not draw text for N/A 
  geom_text(aes(x = 1.5, y = ifelse(sig == "N/A", 1.1, 0.95), label = ifelse(measure_key == "Submissions", "", as.character(sig))), color = "black") +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_grid(author_key ~ measure_key, switch = "y") +
  coord_cartesian(ylim = c(0, 1)) +
  scale_y_continuous(position = "right") +
  theme_dakota() +
  guides(fill = F) +
  labs(
    x = "Gender of Author",
    y = ""
  )
